---
title: "Usage of GitHub Pages at SUB"
author: "Max Held"
date: "First published 2020-03, last updated `r Sys.Date()`"
pkgdown:
  as_is: true
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(metaR)
library(magrittr)
```

## Motivation

[GitHub Pages](https://pages.github.com) lets you serve static websites (HTML5, CSS, JS) right from GitHub.
That can be convenient to publish research results or documentation.

You just need to push your assets to a branch named `gh-pages` or a `docs/` folder on `master`.
The website for, say, project `foo` is then available to the world at `https://subugoe.github.io/foo`.

To learn more about publishing results of your R project to GitHub Pages, see [muggle](http://subugoe.github.io/muggle/).
You can also use [this GitHub Action](https://github.com/maxheld83/ghpages) to publish arbitrary assets to GitHub Pages.


## Existing GitHub Pages Usage at SUB

To potentially transition to a custom domain (see [#4](https://github.com/subugoe/metaR/issues/4)), we first need to know who would be affected by such a change.
(Notice though, that all old URLs would be forwarded automatically, so this is just out of an abundance of caution.)
Here are all repos who currently have a GitHub Page (as defined a `200` status return).

```{r}
repos <- gh::gh(
  endpoint = "GET /users/:username/repos",
  username = "subugoe",
  .limit = Inf
) %>%
  purrr::map_dfr(
    .f = function(x) {
      name <- x$name
      response <- httr::GET(url = paste0("https://subugoe.github.io/", name))
      tibble::tibble(
        name = name,
        status = httr::status_code(x = response),
        has_ghpages = status == 200
      )
    },
    .id = NULL
  )
repos %>%
  dplyr::filter(has_ghpages == TRUE) %>%
  knitr::kable()

# can't get collaborators via API b/c that would require push access to all repos
# gh::gh("GET /repos/:owner/:repo/collaborators", owner = "subugoe", repo = "2019-11-12-ugoe-carpentries", .limit = Inf)
# committers are possible, but are a bad source, b/c they include lots of outside contributors
# gh::gh("GET /repos/:owner/:repo/commits", owner = "subugoe", repo = "2019-11-12-ugoe-carpentries", .limit = Inf)
```
