---
title: "Project Management"
author: "Max Held"
date: "First published 2020-03, last updated `r Sys.Date()`"
pkgdown:
  as_is: true
---

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    echo = FALSE
)
```

```{r setup}
library(metar)
```

GitHub, though primarily a code repository, also has some lightweight project management features.

This document includes some opinionated suggestions for using GitHub as our project management tool.

The project management on GitHub has some advantages, that may lend itself well to our remote and asynchronous work.
It encourages you to think of a project in small chunks, each of which can (or could) be definitively completed.

But project management often degenerates into unproductive "work about work", so skepticism is in order.
**You should never feel obligated to use a tool that does not help you.**
These suggestions are thus merely [focal points](https://en.wikipedia.org/wiki/Focal_point_(game_theory)) for *how* to use GitHub together, *if* you find it useful.
You can also use it partially, or only passively.


## Webinar

We held a related webinar on this topic on 2020-03-06.

You can find the recorded version at:

- `\\ug-sub-fs02.sub.uni-goettingen.de\share\metar` (requires [VPN access](https://intranet.sub.uni-goettingen.de/pages/viewpage.action?pageId=118144269))
- `owncloud.gwdg.de\metar` (requires owncloud access)


## Getting Started

To get started right away:

1. Get an account on GitHub.com.
   Choose a username that is easy to type and to remember for your teammates.
   Assume that the username is public to the world.
   [Customize your notifications](https://help.github.com/en/github/receiving-notifications-about-activity-on-github/choosing-the-delivery-method-for-your-notifications).
   By default, you would get *a lot* of emails.
2. Join our [subugoe](https://github.com/subugoe) organisation on GitHub, by giving your username to one of your teammates or email it to `held@sub.uni-goettingen.de`.
3. You're good to go! You can browse the public SUB repos and their issue trackers at https://github.com/subugoe/ or start dive right into one project, such as https://github.com/subugoe/hybrid_oa_dashboard/issues.


## Documentation

GitHub has extensive documentation about its project management features in different formats:

- [issues guides](https://guides.github.com/features/issues/) (10 mins)
- [issues help](https://help.github.com/en/github/managing-your-work-on-github/managing-your-work-with-issues) (more extensive)

You can learn how to write **GitHub-Flavored Markdown (GFM)**, the (*very* simple) markup language for GitHub issues here:

- [gfm guide](https://guides.github.com/features/mastering-markdown/) (3 mins)
- [gfm help](https://help.github.com/en/github/writing-on-github)

The rest of this document lays out some conventions of how we might be using GitHub project management.


## Organisations and Teams

GitHub knows individual and organisation accounts.
Our organisation is https://github.com/subugoe, which we share with everyone using GitHub at SUB.

Inside the org account, there are (nested) teams.
Teams make it easier to `@`-mention or manage privileges for a group of people at the same time.
Relevant for us are:

- https://github.com/orgs/subugoe/teams/wag for the entire [Abteilung Wissen als Gemeingut](https://www.sub.uni-goettingen.de/kontakt/abteilungen-a-z/abteilungs-und-gruppendetails/abteilunggruppe/wissen-als-gemeingut/)
  - https://github.com/orgs/subugoe/teams/hybrid inside it for the [Hybrid Open Access Dashboards Projekt](https://www.sub.uni-goettingen.de/projekte-forschung/projektdetails/projekt/hybrid-oa-dashboards/)

On the team pages, you can find related repositories, project boards (more on that below) and a discussion page (which we're probably not using).

You can always add more (nested) teams, or add repos to existing teams.

Learn more about organisations and teams [here](https://help.github.com/en/enterprise/2.19/admin/user-management/organizations-and-teams).


## Issues

Project management on GitHub is organised around **"issues"** (otherwise known as "tickets").
Issues are relatively small chunks of work, ideas or problems, such as "add user login".

Issues always belong to *repos* (short for repositories) which is where a particular piece of software is developed.
In our case, some project or publication may reside in a repository, or more.
You can also use GitHub issues on [GitHub.com](https://github.com) without ever touching the code in the repos.
Issues should always be opened in the most appropriate repo, though they can also easily be [moved](https://help.github.com/en/github/managing-your-work-on-github/transferring-an-issue-to-another-repository).

- Issues are **closeable**.
    They should be formulated in such a way that they can either be deemed completed, or rejected, in which case they can be marked as closed.
    Less goal-oriented communication and unclear deliverables are discouraged by the format.
- Issues are **cheap**.
    Issues can easily be created, closed, re-opened, moved etc.
    If in doubt, you can create an issue, as long as it is closeable.
- Issues can be **open to everyone**, so even people outside the organisation can participate.
- **You need not read every, or even most issues**.
    The assumption is that, if something is important, you will be asked to look at it, or find it yourself.
- **Not every, or even most issues need to be closed**.
    Time is finite, but happily, issue backlogs are not.
    Adding an issue can be a good way to get an idea out of your mind that you may or may not ever get around to.
- Issues are **asynchronous**.
    You can react to an issue when it fits your priorities.
    If something needs urgent attention, you can `@-`mention another username or team.
- Issues are quite **powerful**.
    They can be linked, tagged, assigned to milestones or people.

Here are some more suggestions for [how to write good issues](https://wiredcraft.com/blog/how-we-write-our-github-issues/).


### Special Labels

In addition to the default GitHub issue labels, we can use these (they'll look prettier on GitHub.com):

```{r}
knitr::kable(wag_labels())
```

You can set these up in your own repo by once running `use_wag_labels()`.

`needs-votes` is intended to gauge interest / worthiness of an idea *before* committing a lot of time to build it out.
If you have such an idea, just add the `needs-votes` label.
You can see all current issues tagged `needs-votes` with the search query `label:needs-votes org:subugoe` using GitHub's [advanced search](https://help.github.com/en/github/searching-for-information-on-github/about-searching-on-github).
You can also get an overview over all issues at https://github.com/issues.
If you like an idea, react to it using one of the reaction emojis or comment on it.
We may also discuss these in person during weeklies or other meetings.

`placeholder` is for work, which happens in, and is tracked in repositories outside of the `subugoe` org, such as an ropensci package.
You might still want to track that work in a placeholder issue.

To add more special labels, request it in an issue to this package or create a pull request.


### Special Repos

Issues should usually go inside the repo to which they pertain, and from which they can (or could) be closed.

There are some exceptions to this rule for issues without a clear place:

1. https://github.com/subugoe/metar also accepts issues around improving *how we work*.
    For example, an idea to enhance the reproducibility of reports may go here.
    These issues may be "closeable" right within {metar} by adopting some best practice, or they might require some work in another package or even a new package.
2. https://github.com/subugoe/scholcomm_analytics also accepts issues around *what we might work substantively*.
    For example, an idea for a new analysis can be logged here, though it may be done in its own repo, if commited to.
    There is not a really good reason to log these plans in the blog repo, except that this seems to be the going conventions.
    Arguably, new project ideas belong on this landing page, because if completed, the whole project would be listed here.


### Milestones

If you want to, you can also go all-in and enter project timetables and deliverables to GitHub with all the bells and whistles, as I have here done for the [hybrid open access dashboard project](https://github.com/subugoe/hybrid_oa_dashboard).


## Projects

GitHub also offers Kanban-style boards, which are confusingly known as "projects".

Projects are a *view* on existing issues.

Counter to the issues themselves, projects can span issues from *several* repositories, though not from different orgs.

Projects can be a good way to:

- narrow down your focus to a few current issues that are being worked on now
- get a more satisfying card-based UI
- organise several issues across different repos that are all related to some bigger goal.

Projects are also "automated"; the issue cards move around automatically based on their status.

There is so far only one project for us: https://github.com/orgs/subugoe/projects/2
The goal is to give everyone (if they want to know) some idea of what everyone else (if they want to share) is working on.

You can learn about them here:

- [project (aka board) help](https://help.github.com/en/github/managing-your-work-on-github/about-project-boards)
